### 2023-07-28 paper/sec-dis-pseudodata.tex
Start improving kinematic plots
Update kinematic plots

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
    \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-SND.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv2.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
    \caption{\small The event yields per bin, $N_{\rm ev}^{(i)}$, for muon neutrinos at the
      FASER$\nu$, SND@LHC (upper panels), FASER$\nu$2, and FLArE (bottom panels) experiments.
      %
      Selected events are restricted to the DIS region Eq.~(\ref{eq:DISconditions}).
      %
      Only bins with $\ge 30$ events are retained.
	%
	Adding up the bins in each of the panels results into the numbers listed in
	Table~\ref{tab:integrated_rates}.}
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.9\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
    \caption{The kinematic coverage in the $(x,Q^2)$ plane
      of muon neutrino scattering
      at FASER$\nu$2, FLArE,
      and AdvSND (see also Fig.~\ref{fig:fasernu2_muon})
      compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%-----------------------------------------------------------------------
\begin{figure}[t]
    \centering
    \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-SND.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-FASERv2.pdf}
    \includegraphics[width=0.495\textwidth]{plots/FPF-FLArE100.pdf}
    \caption{\small The event yields per bin, $N_{\rm ev}^{(i)}$, for muon neutrinos at the
      FASER$\nu$, SND@LHC (upper panels), FASER$\nu$2, and FLArE (bottom panels) experiments.
      %
      Selected events are restricted to the DIS region Eq.~(\ref{eq:DISconditions}).
      %
      Only bins with $\ge 30$ events are retained.
	%
	Adding up the bins in each of the panels results into the numbers listed in
	Table~\ref{tab:integrated_rates}.
	\textcolor{red}{(To be replaced with the results from the new fluxes, SND $\to$ AdvSND)}}
    \label{fig:fasernu2_muon}
\end{figure}
%-----------------------------------------------------------------------

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.6\textwidth]{plots/KIN_DIS_FPF.pdf}
    \caption{The kinematic coverage in the $(x,Q^2)$ plane
      of muon neutrino scattering
      at FASER$\nu$2, FLArE,
      and AdvSND (see also Fig.~\ref{fig:fasernu2_muon})
      compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
